Stack Safety is a Security Property

### 2021-04-17 tex/main.tex

\ifaftersubmission
\apt{Given that the deferred property suffices to specifcy the lazy policies,
  the case for observable properties is pretty weak.  Should we just cut them?}
\fi

While deferred integrity meaningfully captures the intuition
behind lazy tagging, we seek properties that can be used to evaluate any reasonable
enforcement mechanism. Consider a hypothetical
taint-tracking policy that allows high-security to be copied as long as it is
tagged as such and not exfiltrated, or that allows dangerous writes to be
copied as long as they don't affect critical operations. This calls for
an abstract mechanism to characterize behaviors that are externally relevant.

>>>>

%\apt{Given that the deferred property suffices to specifcy the lazy policies,
%  the case for observable properties is pretty weak.  Should we just cut them?}

While deferred integrity meaningfully captures the intuition
behind lazy tagging, we seek properties that can be used to evaluate the broadest
possible range of reasonable
enforcement mechanisms. Consider a hypothetical
taint-tracking policy that allows high-security to be copied as long as it is
tagged as such and not exfiltrated, or that allows dangerous writes to be
copied as long as they don't affect critical operations. This calls for
an abstract mechanism to characterize behaviors that are externally relevant.
